# Improve {.vertical-center}

Your turn 🎮

## Disable other checks

Modify `shinyValidator::audit_app` parameters:

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "2-5"
shinyValidator::audit_app(
  load_testing = FALSE, 
  profile_code = FALSE, 
  check_reactivity = FALSE
)
```

```{r}
dracula_card(
  borderColor = "red",
  outline = TRUE,
  dracula_text(
    color = "red",
    weight = "bold",
    size = "lg",
    "For learning purposes we disable load test, profiling, ... at the moment ..."
  )
)
```

## Add server testing {auto-animate=true}

```{r}
dracula_card(
  borderColor = "green",
  outline = TRUE,
  dracula_text(
    color = "green",
    weight = "bold",
    size = "lg",
    "Goal: test reactivity and how pieces work together ..."
  )
)
```

```{r}
#| eval: false
#| echo: true
usethis::use_test("app-server-test")
```

## Add server testing {auto-animate=true}

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "|3|4|6|7|8|9"
usethis::use_test("app-server-test")
# Inside app-server-test
testServer(app_server, {
  session$setInputs(obs = 0)
  # There should be an error
  expect_error(output$distPlot)
  session$setInputs(obs = 100)
  str(output$distPlot)
})
# Test it
devtools::test()
```

```{r}
dracula_card(
  borderColor = "red",
  outline = TRUE,
  dracula_text(
    color = "red",
    weight = "bold",
    size = "lg",
    "Server tests are run without the UI, inputs have to be changed manually with session."
  )
)
```

Run `shinyValidator::audit_app` and have a look at the coverage tab.

## Customize Crash test

```{r}
dracula_card(
  borderColor = "green",
  outline = TRUE,
  dracula_text(
    color = "green",
    weight = "bold",
    size = "lg",
    "Goal: UI feature testing. Is the app starting? Is the background dark? ..."
  )
)
```

Leverage `{shinytest2}` power^[See: https://rstudio.github.io/shinytest2/articles/in-depth.html], `app` being the Shiny app to audit. 

::: {.small}
```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "2-5"
shinyValidator::audit_app(
  {
    app$set_inputs(obs = 1000)
    app$get_screenshot("plop.png")
  },
  load_testing = FALSE, 
  profile_code = FALSE, 
  check_reactivity = FALSE
)
```
:::

Run the above code and have a look at the screenshots.

## Output checks (1/3)

```{r}
dracula_card(
  borderColor = "green",
  outline = TRUE,
  dracula_text(
    color = "green",
    weight = "bold",
    size = "lg",
    "Goal: track if an output has changed after a commit..."
  )
)
```

::: {.xsmall}
Create this function in `helpers.R`:

```{r}
#| eval: false
#| echo: true
make_hist <- function(val) {
  hist(rnorm(val))
}
```

Add it to `app_server.R`:

```{r}
#| eval: false
#| echo: true
output$distPlot <- renderPlot({
  make_hist(input$obs)
})
```

Enable output check in `shinyValidator::audit_app`:

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "6"
shinyValidator::audit_app(
  load_testing = FALSE, 
  profile_code = FALSE, 
  check_reactivity = FALSE, 
  output_validation = TRUE
)
```

:::

## Output checks (2/3) {auto-animate=true}

Create a new test:

```{r}
#| eval: false
#| echo: true
usethis::use_test("base-plot")
```

## Output checks (2/3) {auto-animate=true}

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "|2|4|5|6"
usethis::use_test("test-base-plot")
renv::install("vdiffr")
# Inside test-base-plot
test_that("Base plot OK", {
  set.seed(42) # to avoid the test from failing due to randomness :)
  vdiffr::expect_doppelganger("Base graphics histogram", make_hist(500))
})
# Test it
devtools::test()
```

```{r}
dracula_card(
  borderColor = "red",
  outline = TRUE,
  dracula_text(
    color = "red",
    weight = "bold",
    size = "lg",
    "A svg snapshot is created during first run. If you change the plot, snapshots are compared."
  )
)
```

## Output checks (3/3) 

:::: {.columns .small}

::: {.column width="50%"}
1. We slightly modify `make_hist()`:

```{r}
#| eval: false
#| echo: true
make_hist <- function(val) {
  hist(rnorm(val * 2))
}
```

2. Run the test again:

```{r}
#| eval: false
#| echo: true
devtools::test()
```

3. Failure may be reviewed with:

```{r}
#| eval: false
#| echo: true
testthat::snapshot_review('basic-plot')
```

4. Run `shinyValidator::audit_app` and look at the outputs tab.
:::

:::{.column width="50%"}
<iframe src="./assets/output-validation-example/ggplot-validation.html"
title="Output validation widget with {diffviewer}" width="100%" height="550px" style="margin-left: 30px">
</iframe>
:::

::::

## Performance: Code profiling (1/2)

```{r}
dracula_card(
  borderColor = "green",
  outline = TRUE,
  dracula_text(
    color = "green",
    weight = "bold",
    size = "lg",
    "Goal: track any performance bottleneck."
  )
)
```

::: {.xsmall}
Add this function to `helpers.R`^[Stolen with ❤️ from Efficient R programming book: https://csgillespie.github.io/efficientR/programming.html]:

```{r}
#| eval: false
#| echo: true
slow_func <- function(n) {
  vec <- NULL # Or vec = c()
  for (i in seq_len(n))
    vec <- c(vec, i)
  vec
}
```

Add it to `app_server.R`:

```{r}
#| eval: false
#| echo: true
app_server <- function(input, output, session) {
  output$distPlot <- renderPlot({
    slow_func(5*10^4) # you may reduce if needed
    make_hist(input$obs)
  })
}
```

:::

## Performance: Code profiling (2/3)

Modify the custom headless script by adding a __timeout__:

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "3,6"
shinyValidator::audit_app(
  {
    app$set_inputs(obs = 1000, timeout_ = 15 * 1000)
    app$get_screenshot("plop.png")
  },
  timeout = 15,
  load_testing = FALSE, 
  profile_code = TRUE, 
  check_reactivity = FALSE
)
```

Run `shinyValidator::audit_app` and have a look at the profiling tab.

## Performance: Code profiling (3/3)

<iframe src="./assets/code-profile-example/code-profile.html"
title="Output validation widget with {diffviewer}" width="100%" height="550px" style="margin-left: 30px">

## Performance: Load testing (1/2)
:::: {.columns}

::: {.column width="50%"}
```{r}
dracula_card(
  borderColor = "green",
  outline = TRUE,
  dracula_text(
    color = "green",
    weight = "bold",
    size = "lg",
    "Goal: Check if the app can support concurrent user sessions."
  )
)
```
:::

::: {.column width="50%"}
```{r}
dracula_card(
  borderColor = "red",
  outline = TRUE,
  dracula_text(
    color = "red",
    weight = "bold",
    size = "lg",
    "Load testing might not work well at the moment..."
  )
)
```
:::

::::

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "7"
shinyValidator::audit_app(
  {
    app$set_inputs(obs = 1000, timeout_ = 15 * 1000)
    app$get_screenshot("plop.png")
  },
  timeout = 15,
  load_testing = TRUE, 
  profile_code = TRUE, 
  check_reactivity = FALSE
)
```

## Performance: Load testing (2/2)

<iframe src="./assets/load-test-example/load-test.html"
title="Load test report for a non-optimized app." width="100%" height="550px" style="margin-left: 30px">
</iframe>

