# Welcome {.vertical-center}

## Hi, I am David Granjon

Senior Software developer at Novartis.

```{r}
tagAppendAttributes(
  dracula_avatar("assets/images/jpeg/david.jpeg"),
  style = "height: 5.4em; width: 5.5em;"
)
```

We're in for 2 hours of **fun**!

- Grab a `r ji("coffee")`
- Make yourself comfortable `r ji("couch")` or 🧘
- Ask questions `r ji("question")`  

## Program

1. Introduction __10  min__
2. Setup {shinyValidator} __20 min__
3. Discover {shinyValidator} __30 min__
4. Customize {shinyValidator} __40 min__
5. Add CI/CD (if time allows)
6. Q&A

## Workshop Material

- Slides: [https://rinpharma2022.rinterface.com/](https://rinpharma2022.rinterface.com)

Clone this repository with the RStudio IDE or via the command line.

```bash
git clone https://github.com/RinteRface/rinpharma2022.git
cd rinpharma2022
```

Then run `renv::restore()` to install the dependencies.

## Pre-requisites

If you want to run `{shinyValidator}` locally (not on CI/CD), you must have:

- `shinycannon` installed for the load-test part. See [here](https://rstudio.github.io/shinyloadtest/articles/shinycannon.html).
- A chrome browser installed like [chromium](https://www.chromium.org/getting-involved/download-chromium/). 

- `git` installed and a [GitHub](https://github.com/) account.

```{r}
dracula_card(
  borderColor = "red",
  outline = TRUE,
  dracula_text(
    color = "red",
    weight = "bold",
    size = "lg",
    "This workshop is recorded. If it does not work for you, it is better to listen and stay on track. Fear not! You can retry later on your side with the recording. "
  )
)
```
