---
title: My Slide Show
subtitle: '`r Sys.Date()`'
author: "David Granjon, Novartis"
format: 
  revealjs:
    css: "styles/dracula-ui.css"
    theme: "dracula.scss"
    echo: true
    code-link: true
    footer: "Novartis, 2022"
    template-partials: 
      - title-slide.html
highlight-style: dracula
---

```{r setup, include = FALSE}
library(emo)
```

## Program
We're in for 2 hours of **fun**!

- Grab a `r ji("coffee")`
- Make yourself comfortable `r ji("couch")` or 🧘
- Ask questions `r ji("question")`  

1. Introduction 				__5  min__
2. Setup {shinyValidator} __45 min__
3. Analyse {shinyValidator} report __45 min__
4. Questions

## Quarto

<div class="drac-box drac-card drac-bg-purple drac-p-sm">
  <span class="drac-text drac-line-height drac-text-black">Dracula</span>
</div>

:::: {.columns}

::: {.column width="40%"}
contents...
:::

::: {.column width="60%"}
contents...
:::

::::

## Bullets

::: {.panel-tabset}

### Tab A

[Preview](https://example.com){preview-link="true"}

### Tab B

Content for `Tab B`

:::

## Code

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
#| output-location: column-fragment
#| code-line-numbers: "|2"

library(ggplot2)

1+1
```
