---
title: My Slide Show
subtitle: '`r Sys.Date()`'
author: "David Granjon, Novartis"
format: 
  revealjs:
    css: "assets/styles/dracula-ui.css"
    theme: "assets/styles/dracula.scss"
    code-link: true
    code-copy: true
    footer: "Novartis, 2022"
    navigation-mode: vertical
    controls-layout: bottom-right
    controls-tutorial: true
    template-partials: 
      - title-slide.html
highlight-style: dracula
---

```{r setup, include = FALSE}
library(emo)
library(dRacula)
```

# Welcome

We're in for 2 hours of **fun**!

- Grab a `r ji("coffee")`
- Make yourself comfortable `r ji("couch")` or 🧘
- Ask questions `r ji("question")`  

## Program

1. Introduction 				__5  min__
2. Setup {shinyValidator} __45 min__
3. Analyse {shinyValidator} report __45 min__
4. Questions

## Workshop Material

- Slides: [https://rinpharma2022.rinterface.com/](https://rinpharma2022.rinterface.com)

Clone this repository with the RStudio IDE or via the command line.

```bash
git clone https://github.com/RinteRface/rinpharma2022.git
cd rinpharma2022
```

Then run `renv::restore()` to install the dependencies.

# Introduction

## Clothes don't make the man

```{r}
dracula_card(
  borderColor = "red",
  outline = TRUE,
  class = "drac-mt-lg",
  dracula_p(
    "Your app may be as beautiful and as cool as you want, it is useless if it does not start/run."
  )
)
```

## From prototype to production

How do we transition❓

:::: {.columns}

::: {.column width="33%"}
```{r}
dracula_card(
  outline = TRUE,
  dracula_p(
    dracula_text(
      "Reliable", 
      color = "purple",
      weight = "bold"
    ), 
    ": is the app doing what it is intended to do?"
  )
)
```
:::

::: {.column width="33%"}
```{r}
dracula_card(
  outline = TRUE,
  borderColor = "orange",
  dracula_p(
    dracula_text(
      "Stable", 
      color = "orange",
      weight = "bold"
    ), 
    ": how often does it crash?"
  )
)
```
:::

::: {.column width="33%"}
```{r}
dracula_card(
  outline = TRUE,
  borderColor = "green",
  dracula_p(
    dracula_text(
      "Available", 
      color = "green",
      weight = "bold"
    ), 
    ": is the app fast enough to handle multiple concurrent users?"
  )
)
```
:::

::::

In practice, a few apps meet all these requirements 😈. 

## Available tools

::: {.panel-tabset}

### Structure your app

<img src="assets/images/svg/golem.svg" width="10%" style="display: block; margin: auto;" class="svg-img"/>

- Easier checking, linting, documentation and testing.
- Just ... __easier__. 😀

### __dependencies__

<img src="assets/images/svg/renv.svg" width="10%" style="display: block; margin: auto;" class="svg-img"/>

- Fix package versions.
- Increased __reproducibility__.

### __Test__ code

<img src="assets/images/svg/testthat.svg" width="10%" style="display: block; margin: auto;" class="svg-img"/>

- Unit tests: test business logic. 
- Server testing: test how Shiny modules or pieces work together (with reactivity).
- UI testing: test UI components, snapshots, headless-testing (`{shinytest2}`).

### Optimize
Are there bottlenecks?

- __Load__ testing: How does the app behave with 10 simultaneous user? `{shinyloadtest}`.
- __Profiling__: What part of my app is slow?`{profvis}`.
- Reactivity: Are there any reactivity issues? <img src="assets/images/svg/reactlog.svg" width="10%" style="display: inline; margin: auto;" class="svg-img"/>.

:::

## Automate: CI/CD

::: {.panel-tabset}
### What

- Continuous integration: automatically __check__ new features. 🏥
- Continuous deployment: automatically __deploy__ content. ✉️
- Running on a __remote__ environment ☁️:
  - [Github Actions](https://github.com/features/actions).
  - [Jenkins](https://www.jenkins.io/).
  - [Gitlab CI/CD](https://docs.gitlab.com/ee/ci/).

### Benefits

- __Automated__.
- More __reproducible__ (more os/R flavors available).
- __Time saver__.
- Less duplication.

### How? 
Not easy 😢

- Select __DevOps__ platform (GitLab, GitHub, ...).
- Add __version control__ (git knowledge).
- Build custom GitLab runner (optional).
- Write __CI/CD instructions__ (better support for GitHub).
- Enjoy ...

Can't we make things easier❓

:::

## Stop ... I am lost ...

<img src="assets/images/svg/sad.svg" width="40%" style="display: block; margin: auto;" class="svg-img"/>

- There are just so many tools! How to use them properly?
- Is there a way to __automate__ all of this? I just don't have time ... 😞

## Welcome {shinyValidator}

- Integrate all previous mentioned tools.
- Produces a single HTML report output.
- Flexible.

# Setup {shinyValidator}

## {golem} {auto-animate=true}

```{r}
#| eval: false
#| echo: true
path <- file.path(tempdir(), "mypkg") 
golem::create_golem(path)
# ...
```

## {golem} {auto-animate=true}

```{r}
#| eval: false
#| echo: true
path <- file.path(tempdir(), "mypkg") 
golem::create_golem(path)
usethis::use_mit_license() # or whatever license
usethis::use_testthat()
usethis::use_test("dummy")
usethis::use_git()
usethis::use_github() # make sure to have a valid GITHUB_PAT
# ...
```

## {renv} {auto-animate=true}

```{r}
#| eval: false
#| echo: true
system("echo 'RENV_PATHS_LIBRARY_ROOT = ~/.renv/library' >> .Renviron")
```

## {renv} {auto-animate=true}

```{r}
#| eval: false
#| echo: true
system("echo 'RENV_PATHS_LIBRARY_ROOT = ~/.renv/library' >> .Renviron")

# SCAN the project and look for dependencies
renv::init()
# install missing packages
renv::install("<PACKAGE>")
# Capture new dependencies after package installation
renv::snapshot()
```

## Install {shinyValidator}

```{r}
#| eval: false
#| echo: true
devtools::install_github("Novartis/shinyValidator")
library(shinyValidator)
## At the root of your R package
use_validator("github")
devtools::document() # update help
renv::snapshot()
```

# {shinyValidator}: step by step

## Some graphs with mermaid

```{mermaid}
%%{init: {'theme':'dark'}}%%
flowchart LR
  A[Hard edge] --> B(Round edge)
  B --> C{Decision}
  C --> D[Result one]
  C --> E[Result two]
```
